---
title: "Untitled"
author: "Sahil, Ariel, Ilya, Lekha, Anthony, Trang"
date: "4/26/2021"
output: pdf_document
---

## Introduction

Trang.

## Loading R packages

```{r}
library(foreign) # Allows us to import data from common statistical packages
library(ggplot2) # Used for plotting data
library(grid) # Used to arrange plots of data
library(gridExtra) # Used to arrange plots
library(rugarch) # Used for creating Garch models
library(quantmod) # Used for plotting time series 
library(fGarch) # Used to estimate variance 
library(dynlm) # Used to estimate mean equation 
library(tidyverse) #Used for data manipulation
library(FinTS) # Used to perform Arch test and check ARCH effects
theme_set(theme_bw())
```

## Formula and Basics

Trang.

## Data description

+ FB.Open: The opening price of 1 share (in USD) of facebook once the market opens
+ FB.High: The highest price of 1 share (in USD) of facebook on the given day 
+ FB.Low: The lowest price of 1 share (in USD) of facebook on the given day 
+ FB.Close: The closing price of 1 share (in USD) of facebook once the market closes
+ FB.Volume: The number of shares of facebook traded on the given day 
+ FB.adjusted: The adjusted closing price of 1 share (in USD) of facebook after accounting corporate actions

```{r}
# FB data-set
fb <- getSymbols("FB", auto.assign = F)
nrow(fb) # Gives you the number of data points

# FB data-set
fb.df <- as.data.frame(fb)


# Renaming the phantom "Date" column
fb.df <- cbind(Date = rownames(fb.df), fb.df)
rownames(fb.df) <- 1:nrow(fb.df)

fb_train_data = fb.df[1:2100,]
fb_test_data = fb.df[2100:2247,]
```


## Visualization

Ilya, can you write 1-2 sentences about the visualization?

```{r}
# FB data-set
chartSeries(fb) # Plots the time series
```

## Analysis

```{r}
# FB data-set
fb_plot_1 <- ggplot(fb.df, aes(y = FB.Adjusted, x = Date)) + geom_line(col = 'blue', group = 1) + labs(ylab = 'return', xlab = 'Time', title = 'Adjusted Returns')

grid.arrange(fb_plot_1, ncol = 2);
```

```{r}
# FB data-set
# Examine the FB's daily stock returns trend
fb.df$Date <- seq.Date(as.Date('2010-01-01'), by = 'day', length.out = length(fb.df$FB.Adjusted))
ggplot(fb.df, aes(y = FB.Adjusted, x = Date )) + geom_line(col = 'red', group = 1) +
  labs(title = 'FB daily Stock Returns', ylab = 'return')
```

## Model Evaluation

```{r}
# Step 1: Estimate mean equation r = beta + error
fb_data_mean <- dynlm(FB.Adjusted ~ 1, data = fb_train_data)

# Step 2: Retrieve the residuals from the former model and square them
ehatsq <- ts(resid(fb_data_mean)^2)

# Step 3: regress squared residuals on one-lagged squared residuals
fb_data_arch <- dynlm(ehatsq ~ L(ehatsq), data = ehatsq)

summary(fb_data_arch)
```


```{r}
# FB data-set
fb_data_archTest <- ArchTest(fb_train_data$FB.Adjusted, lags = 1, demean = TRUE)
fb_data_archTest

#Reject Null Hypothesis
```
Because the p-value is < 0.05, we reject the null hypothesis and conclude the presence of ARCH(1) effects.

```{r}
# FB data-set
# Plot the conditional variance
fb_arch_fit <- garchFit(~garch(1,0), data = fb_train_data$FB.Adjusted, trace = F)

summary(fb_arch_fit)

fb_pred <- predict(fb_arch_fit, n.ahead = 100, trace = TRUE, mse = c("cond","uncond"),
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)

summary(fb_pred)

fb_train_data$ht <- fb_arch_fit@h.t
# How to rename the first column as "Date"?
ggplot(fb_train_data, aes(y = ht, x = Date)) + geom_line(col = '#ff9933', group = 1) + ylab('Conditional Variance') + xlab('Date')
```
Looking at the graph, you can see the periods in which volatility was high.

## Prediction and Model Accuracy

```{r}
# FB data-set
# We can change the armaOrder to create different models and keep the model with lowest AIC!

# 1st Model: AIC = 4.0681
fb1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder = c(1, 1)), distribution.model = "std")

fbGarch1 <- ugarchfit(spec = fb1, data = fb_train_data$FB.Adjusted)

# 2nd Model: AIC = 10.437
fb2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder = c(0, 0)), distribution.model = "std")

fbGarch2 <- ugarchfit(spec = fb2, data = fb.df$FB.Adjusted)

# 3rd Model: Does not converge
fb3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder = c(1, 0)), distribution.model = "std")

fbGarch3 <- ugarchfit(spec = fb3, data = fb.df$FB.Adjusted)

# 4th Model: AIC = 9.2589
fb4 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder = c(0, 1)), distribution.model = "std")

fbGarch4 <- ugarchfit(spec = fb4, data = fb.df$FB.Adjusted)
```
From the above computations, we say that fGarch 3 was a better model as it has an AIC = 4.2241, which is the lowest amongst the rest. We will use this model to make predictions.

```{r}
# FB data-set 
# Finally forecast whatever you want!
# This is an example of what you want to forecast where n.ahead is the number of predictions you want to make and fbGarch3 is an example for the model that you want to use.
fbPredict <- ugarchboot(fbGarch1, n.ahead = 10, method = c("Partial", "Full")[1])
fbPredict
plot(fbPredict, which = 2)
plot(fb_test_data$FB.Adjusted, xlab="Forecasted days ahead", ylab="Adjusted", main="FB Forecast")

pred <- as.data.frame(as.table(fbGarch4@fit$fitted.values))
pred <- pred[1:10, ]
testPred <- as.data.frame(fb_test_data)
testPred <- testPred[1:10, ]
mean(abs((pred$Freq-testPred$FB.Adjusted)/pred$Freq)) # Prediction Error
```

## Conclusion

Trang and Lekha

## Reference

https://rpubs.com/cyobero/arch

